Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-14 optim.qmd
changes that might need to be dropped

```{r}
#| label: fig-projection
#| fig.height: 6
#| fig.width: 10
#| fig.cap: Best projections found by the JS opitmiser in each simulation, sorted by the index value. The projection pursuit problem is to detect the 6D sine-wave structure using the spline index. Most simulations have detected a clear sine-wave pattern, while the last six show a straight line with clustering at the ends.. In this simulation, the success rate is 0.88 (44/50).
set.seed(123456)
sin1000 <- spinebil::sinData(6, 1000) %>% scale() %>% as_tibble()
colnames(sin1000) <- paste0("V", 1:6)

>>>>

```{r}
#| label: fig-projection
#| fig.height: 6
#| fig.width: 10
#| fig.cap: Best projections found by the JS opitmiser in each simulation, sorted by the index value. The projection pursuit problem is to detect the 6D sine-wave structure using the spline index. Most simulations have detected a clear sine-wave pattern, while the last six show a straight line with clustering at the ends.. In this simulation, the success rate is 0.88 (44/50).
set.seed(123456)
sin1000 <- spinebil::sinData(6, 1000) %>% scale() %>% as_tibble()
colnames(sin1000) <- paste0("V", 1:6)
#remotes::install_github("uschiLaa/spinebil")
#load(here::here("data/sine_dcor2d_best.rda"))
#load(here::here("data/sin1000.rda"))
#set.seed(123456)
#sin1000 <- spinebil::sinData(6, 1000) %>% scale() %>% as_tibble()
#colnames(sin1000) <- paste0("V", 1:6)
